### 2025-11-10 Proposals/2025-NSF-EntropicGeometry/NarrativeBody.tex
Change Project Summary based on feedback from Alejandro; add Physics and Math affiliations to header
Change file type in mention of Gabriele's biosketch as a separate document

\begin{center}
	\textbf{An axiomatic basis for entropic structures in physical theories} \\
	Christine A. Aidala (PI) and Alejandro Uribe (Co-PI), University of Michigan
\end{center}
%\vspace{-8mm}

@@

Carcassi is the co-initiator with Aidala and technical lead for the Assumptions of Physics program.  He is the Co-PI on the Templeton Foundation grant with Aidala.  Related to the AoP program, he has given seminars to audiences of physicists, mathematicians, and philosophers at places including Harvard, Caltech, Oxford (UK) the University of Pavia (Italy) the Munich Center for Mathematical Philosophy (Germany) and the Wolfram Institute.  He and Aidala gave a joint public talk on misconceptions in the foundations of physics for the Michigan State University Advanced Studies Gateway, and he will give a U-M Saturday Morning Physics public talk on ``What is classical and what is quantum?'' in November 2025.  He was invited and will deliver an overview talk on the AoP program at a special session of the Joint Mathematics Meeting in January 2026.  His training in computer science and engineering allows him to bring ideas from fields not typically studied by individuals trained primarily in mathematics or physics, for example from information theory, theoretical computer science, systems theory, signal processing, and operations research.  His position as U-M Physics Department staff without teaching responsibilities provides him with time and flexibility to dedicate to research related to the AoP program such as the work proposed here. See also his biographical sketch included as an Other Supplementary Document.\\

>>>>

\begin{center}
	\textbf{An axiomatic basis for entropic structures in physical theories} \\
	Christine A. Aidala (PI, Physics) and Alejandro Uribe (Co-PI, Mathematics) \\ 
	University of Michigan
\end{center}
%\vspace{-8mm}

@@

Carcassi is the co-initiator with Aidala and technical lead for the Assumptions of Physics program.  He is the Co-PI on the Templeton Foundation grant with Aidala.  Related to the AoP program, he has given seminars to audiences of physicists, mathematicians, and philosophers at places including Harvard, Caltech, Oxford (UK) the University of Pavia (Italy) the Munich Center for Mathematical Philosophy (Germany) and the Wolfram Institute.  He and Aidala gave a joint public talk on misconceptions in the foundations of physics for the Michigan State University Advanced Studies Gateway, and he will give a U-M Saturday Morning Physics public talk on ``What is classical and what is quantum?'' in November 2025.  He was invited and will deliver an overview talk on the AoP program at a special session of the Joint Mathematics Meeting in January 2026.  His training in computer science and engineering allows him to bring ideas from fields not typically studied by individuals trained primarily in mathematics or physics, for example from information theory, theoretical computer science, systems theory, signal processing, and operations research.  His position as U-M Physics Department staff without teaching responsibilities provides him with time and flexibility to dedicate to research related to the AoP program such as the work proposed here. See also his biographical sketch included as Other Personnel Biographical Information.\\
